Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-05-28 article.tex
Break line after 80 char
remove duplicate
add some defect of optical devices

% BG : brain, complex organ
Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease, epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain.
The human brain is a complex biological organ, which is formed by 100
billions of neurons with 7000 synaptic connections on average. Inferring the
neuron connectivity network through dissection would be an impossible
and daunting task.

% Issue : we have data, but need to have to infer the connectome
% TODO Shed light on the difficulty of the inverse problem:
% noise, time scale (optical imaging speed vs neuron speed), decay of
% fluorescent signal.
Cutting edge optical devices [todo cite] allows to track simultaneously
the neural activity of thousands of neurons through the fluorescent
calcium indicator. The neuron connectivity network could be inferred
from those neuron activity signals.

The neural connectivity inference consists in highlighting, from observational data, direct relationships between neurons. One way to emphasize the connections between neurons is to represent them by a (un)directed graph with $p$ nodes, where each node represents a neuron, and an edge $e_{ij}$ which represents a direct link from neuron  $i$ to neuron $j$. If the graph is undirected, then $e_{ij}$ is equal to $e_{ji}$  for all $i,j$.

>>>>

% BG : brain, complex organ
Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease, epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain.
The human brain is a complex biological organ, which is formed by 100
billions of neurons with 7000 synaptic connections on average. Inferring the
neuron connectivity network through dissection would be an impossible
and a daunting task.

% Issue : we have data, but need to have to infer the connectome
Cutting edge optical devices [todo cite] allows to track simultaneously
the neural activity of thousands of neurons through the fluorescent
calcium indicator. Those devices have however a sampling rate smaller
than the neuron firing speed and takes only two dimensional image, which may lead
to superpose the activity of different neurons. Furthermore, the
decay of the fluorescent calcium signal is slow compare to its rise.
The neural connectivity inference consists in highlighting, from observational
data, direct relationships between neurons. One way to emphasize the
connections between neurons is to represent them by a (un)directed graph with
$p$ nodes, where each node represents a neuron, and an edge $y_{ij}$ which
represents a direct link from neuron  $i$ to neuron $j$. If the graph is
undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
